---
title: "Publications"
output:
  distill::distill_article:
---

```{r setup, echo=FALSE}
library(fontawesome)
knitr::opts_chunk$set(echo = TRUE)
orcid <- "0000-0001-7867-7159"
gscholar <- "xN83U3oAAAAJ"
rgate <- "Thibault-Lovey"
knitr::asis_output(paste0(
  '<p>',
  '<span style="font-size: larger; font-weight: bold;">Thibault Lovey, MD</span><br>',
  'PhD candidate<br>',
  'Epidemiology, Biostatistics and Prevention Institute (EBPI)<br>',
  'University of Zürich (UZH)<br>',
  'Switzerland<br>',
  fontawesome::fa("envelope"), ' <a href="mailto:thibault.lovey@uzh.ch">thibault.lovey@uzh.ch</a>',
  '</p>'
))
```
```{r googlescholar, echo=FALSE}
knitr::asis_output('<link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/academicons@1.9.1/css/academicons.min.css">')
scholarid<-scholar::get_profile("xN83U3oAAAAJ")
knitr::asis_output(paste("<br>Citations: ", scholarid$total_cites, "&nbsp;|&nbsp;&nbsp;h-index: ", scholarid$h_index, "&nbsp;|&nbsp;&nbsp;i10-index: ", scholarid$i10_index))
knitr::asis_output(paste0(
  '<div style="display: flex; justify-content: flex-start;">',
  '<a href="https://orcid.org/', orcid, '" style="text-decoration: none; color: inherit;">',
  '<div style="display: flex; align-items: center; border: 1px solid #ddd; padding: 10px; margin-right: 10px; border-radius: 5px;">',
  '<div style="margin-right: 10px;">',
  fontawesome::fa("orcid", fill = "green"), 
  '</div>',
  'ORCID',
  '</div>',
  '</a>',
  '<a href="https://scholar.google.com/citations?user=', gscholar, '" style="text-decoration: none; color: inherit;">',
  '<div style="display: flex; align-items: center; border: 1px solid #ddd; padding: 10px; margin-right: 10px; border-radius: 5px;">',
  '<div style="margin-right: 10px;">',
  '<i class="ai ai-google-scholar"></i>', 
  '</div>',
  'Google Scholar',
  '</div>',
  '</a>',
  '<a href="https://www.researchgate.net/profile/', rgate, '" style="text-decoration: none; color: inherit;">',
    '<div style="display:flex;align-items:center;border:1px solid #ddd;padding:10px;border-radius:5px;">',
    '<div style="margin-right:10px;">',
    '<i class="ai ai-researchgate"></i>',
    '</div>',
    'ResearchGate',
    '</div>',
    '</a>',
    '</div>'
))
```
<aside>
Source: Google Scholar
</aside>

## Peer-reviewed

Deuel, J. W., Lauria, E., **Lovey, T.**, Zweifel, S., Meier, M. I., Züst, R., Gültekin, N., Stettbacher, A., & Schlagenhauf, P. (2022). Persistence, prevalence, and polymorphism of sequelae after COVID-19 in unvaccinated, young adults of the Swiss Armed Forces: A longitudinal, cohort study (LoCoMo). *The Lancet Infectious Diseases*, 22(12), 1694–1702.
<br>doi:[10.1016/S1473-3099(22)00449-2](https://doi.org/10.1016/S1473-3099(22)00449-2)&nbsp;&nbsp;preprint: [10.1101/2022.02.11.22270836](https://doi.org/10.1101/2022.02.11.22270836)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/PIIS1473309922004492.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1016/S1473-3099(22)00449-2"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1016/S1473-3099(22)00449-2" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>
Ferretti, A., Hedrich, N., **Lovey, T.**, Vayena, E., & Schlagenhauf, P. (2021). Mobile apps for travel medicine and ethical considerations: A systematic review. *Travel Medicine and Infectious Disease*, 43, 102143. <br>doi:[10.1016/j.tmaid.2021.102143](https://doi.org/10.1016/j.tmaid.2021.102143)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/1-s2.0-S1477893921001848-main.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1016/j.tmaid.2021.102143"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1016/j.tmaid.2021.102143" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

**Lovey, T.**, Bielecki, M., Gültekin, N., Stettbacher, A., Muggli, F., Stanga, Z., Farnham, A., Deuel, J., & Schlagenhauf, P. (2022). Illness tracking in SARS-CoV-2 tested persons using a smartphone app: A non-interventional, prospective, cohort study. New Microbes and New Infections, 46, 100967. <br>doi:[10.1016/j.nmni.2022.100967](https://doi.org/10.1016/j.nmni.2022.100967)&nbsp;&nbsp;preprint: [10.2139/ssrn.4003916](https://doi.org/10.2139/ssrn.4003916)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/1-s2.0-S2052297522000191-main.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1016/j.nmni.2022.100967"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1016/j.nmni.2022.100967" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

**Lovey, T.**, O’Keeffe, P., & Petignat, I. (2021). Basic Medical Training for Refugees via Collaborative Blended Learning: Quasi-Experimental Design. Journal of Medical Internet Research, 23(3), e22345. <br>doi:[10.2196/22345](https://doi.org/10.2196/22345)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/PDF.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.2196/22345"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.2196/22345" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

Buchs, A., Conde, A., Frank, A., Gottet, C., Hedrich, N., **Lovey, T.**, Shindleman, H., & Schlagenhauf, P. (2022). The threat of dengue in Europe. New Microbes and New Infections, 49–50, 101061.
<br>doi:[10.1016/j.nmni.2022.101061](https://doi.org/10.1016/j.nmni.2022.101061)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/1-s2.0-S2052297522001135-main.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1016/j.nmni.2022.101061"></div>
::: 
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1016/j.nmni.2022.101061" data-style="small_circle"></span><script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::::
<hr>

Hedrich, N., **Lovey, T.**, Kuenzli, E., Epéron, G., Blanke, U., & Schlagenhauf, P. (2023). Infection tracking in travellers using a mobile app (ITIT): The pilot study. Travel Medicine and Infectious Disease, 52, 102526. 
<br>doi:[10.1016/j.tmaid.2022.102526](https://doi.org/10.1016/j.tmaid.2022.102526)&nbsp;&nbsp;preprint: [10.2139/ssrn.4282958](https://doi.org/10.2139/ssrn.4282958)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/1-s2.0-S1477893922002721-main.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1016/j.tmaid.2022.102526"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1016/j.tmaid.2022.102526" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

O’Keeffe, P., & **Lovey, T.** (2023). Meaningful higher education in Kakuma refugee camp: A case study of why context and contextualization matter. PROSPECTS, 53(1–2), 101–114.
<br>doi:[10.1007/s11125-022-09610-z](https://doi.org/10.1007/s11125-022-09610-z)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/s11125-022-09610-z.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1007/s11125-022-09610-z"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1007/s11125-022-09610-z" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

**Lovey, T.**, Hasler, R., Gautret, P., & Schlagenhauf, P. (2023). Travel-related respiratory symptoms and infections in travellers (2000–22): A systematic review and meta-analysis. Journal of Travel Medicine, taad081. 
<br>doi:[10.1093/jtm/taad081](https://doi.org/10.1093/jtm/taad081)&nbsp;&nbsp;preprint: [10.2139/ssrn.4381176](https://doi.org/10.2139/ssrn.4381176)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/taad081.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.1093/jtm/taad081"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.1093/jtm/taad081" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

**Lovey, T.**, & Schlagenhauf, P. (2023). Augmentation des températures et menace du paludisme en Europe: Un retour indésirable? Revue Médicale Suisse, 19(825), 849–852.
<br>doi:[10.53738/REVMED.2023.19.825.849](https://doi.org/10.53738/REVMED.2023.19.825.849)
&nbsp;&nbsp;[{{< fa download >}} PDF](papers/849-52_44377.pdf)

:::: {.columns}
::: {.column width="10%"}
<div data-badge-type="donut" class="altmetric-embed" data-badge-popover="right" data-doi="10.53738/REVMED.2023.19.825.849"></div>
:::
::: {.column width="10%"}
<span class="__dimensions_badge_embed__" data-doi="10.53738/REVMED.2023.19.825.849" data-style="small_circle"></span>
    <script async src="https://badge.dimensions.ai/badge.js" charset="utf-8"></script>
:::
::: {.column width="80%"}
:::
::::
<hr>

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>